Identifying Equivalent State Bills through Text Reuse. \large Subtitle.

### 2015-11-11 manuscript/text_reuse.tex
updated ms

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{hyperref}

@@

>>>>

\usepackage{graphicx} % to include pictures
\usepackage{subfig} % create subfigures within figures
\usepackage{pdflscape} % e.g. to rotate one page of the document
\usepackage{booktabs} % make better looking tabels with different line types and stuff
\usepackage[left=2.5cm,right=3cm,top=3cm,bottom=2.5cm]{geometry}
\usepackage{fancyhdr} % for pages with custom headers and footers
\usepackage[utf8]{inputenc}
\usepackage{float}
\usepackage{datetime}
\usepackage{natbib}
\usepackage{setspace}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{rotating}
\usepackage{amsmath}
\usepackage{hyperref}

@@

\subsection{Topic Modeling}

Topics of 20 inferred on 200,000 alignments.

\begin{sidewaystable}
\centering
\scalebox{.425}{
\begin{tabular}{rllllllllllllllllllll}
  \hline
 & 0.135 & 0.119 & 0.087 & 0.073 & 0.067 & 0.058 & 0.054 & 0.053 & 0.043 & 0.043 & 0.041 & 0.037 & 0.034 & 0.033 & 0.032 & 0.027 & 0.026 & 0.021 & 0.012 & 0.007 \\ 
  \hline
1 & board & state & general & tax & state & property & section & child & means & health & medical & vehicle & employer & states & feet & benefit & commission & insurer & salts & state \\ 
  2 & department & enacted & assembly & section & court & person & information & person & sale & care & person & insurance & individual & united & distance & school & state & insurance & isomers & party \\ 
  3 & state & legislature & senate & income & order & principal & electronic & abortion & product & patient & department & motor & employee & state & amended & corporation & interstate & commissioner & substances & ring \\ 
  4 & public & people & enacted & amount & person & interest & statement & medical & person & plan & applicant & policy & employment & member & point & public & compact & information & substance & consumer \\ 
  5 & education & section & state & year & action & power & act & woman & manufacturer & services & patient & portable & service & presidential & read & student & member & section & preparation & jwh \\ 
  6 & county & act & appointed & qualified & section & real & notice & parent & device & section & license & electronics & work & official & section & charter & states & company & compound & nurse \\ 
  7 & services & firearm & house & revenue & law & company & date & degree & products & physician & marijuana & coverage & employees & election & south & district & rules & policy & mixture & substituted \\ 
  8 & program & amended & members & taxable & violation & attorney & security & age & dealer & provider & qualifying & person & business & vote & west & director & compacting & association & controlled & extent \\ 
  9 & director & read & member & credit & support & trust & record & physical & including & medical & identification & driver & performed & agreement & north & section & effective & contract & chemical & food \\ 
  10 & office & ammunition & force & code & attorney & agent & subsection & physician & food & individual & application & travel & benefits & president & line & students & duties & state & quantity & practice \\ 
  11 & local & represented & representatives & years & enforcement & agreement & provided & section & facility & act & registration & insurer & period & popular & minutes & specific & bylaws & life & material & indole \\ 
  12 & agency & york & task & investment & jurisdiction & authority & service & death & equipment & person & section & vendor & services & votes & degrees & purpose & date & subsection & schedule & methyl \\ 
  13 & fund & firearms & governor & internal & proceeding & owner & address & performed & drug & treatment & card & transportation & labor & slate & east & directors & law & financial & including & licensure \\ 
  14 & year & texas & speaker & community & petition & entity & effective & means & retail & licensed & registry & customer & compensation & national & seconds & general & provided & contracts & specifically & information \\ 
  15 & division & relating & committee & excess & subsection & means & financing & family & sold & coverage & registered & commercial & section & constitution & street & articles & act & subject & oil & compact \\ 
  16 & health & chapter & court & percent & tribunal & business & person & abuse & energy & practice & gift & service & sex & article & code & interests & article & person & plant & agency \\ 
  17 & secretary & arizona & commonwealth & january & act & limited & number & condition & distributor & provide & information & enrolled & race & elector & traffic & religious & members & including & listed & states \\ 
  18 & fiscal & manufactured & president & date & civil & act & law & drug & system & qualified & caregiver & liability & time & number & adding & officer & rule & risk & grams & home \\ 
  19 & provide & related & term & entity & subject & liability & debtor & unborn & property & provided & criminal & company & sexual & chief & intersection & report & person & documents & excepted & substitution \\ 
  20 & city & federal & resolved & beginning & party & estate & days & years & include & means & board & section & organization & candidate & quarter & person & executive & report & milligrams & reporting \\ 
   \hline
\end{tabular}
}
\end{sidewaystable}
